The Folly of Password Policies: The case for organisations implementing technical alternatives over trying to manage users

### 2014-12-15 paper.tex
Cut even more words out.

These authentication requirements are largely driven by
several desires:

\begin{itemize}
  \item to prevent use of systems by non-employees;
  \item to maintain an audit trail of employees' usage;
  \item to protect company secrets and intellectual property;
  \item to safeguard the personal information of customers and employees; and
  \item to prevent economic and reputational damage from would-be attackers.
\end{itemize}

Additional security in any system normally comes with additional costs
in terms of usability for users and in financial terms for the organisation
that must implement any security processes and policies. In this paper, we
argue that these benefits are primarily for the organisation more than the
users, so are the usability and effort costs placed on users justifiable
if they are to gain very little?

@@

\textcite{herley2009so} argued that users rationally reject costs
placed upon them from security policies. He invokes Kuhn's
``Paradigm Shift''\parencite{kuhn1962structure} to suggest
an imminent, yet dramatic change in
how users are asked to authenticate as the complexity of
rules placed on users increases with each attack.

@@

Password-protected accounts are vunerable to at least three
classes of attack \parencite{florencio2014password}:

\begin{itemize}
  \item Malware infection or other direct compromise of the client machine (e.g. keyloggers)
  \item Attacker learns the passwords via phishing, brute-force guessing or other means
  \item Access to a particular system is gained without the actual password (e.g session hijacking, cross-site request forgery)
\end{itemize}

>>>>

Additional security in any system normally comes with additional costs
in terms of usability for users and in financial terms for the organisation
that must implement any security processes and policies. In this paper, we
argue that these benefits are primarily for the organisation more than the
users. This calls into question the justifiability of placing
effort and usability costs on users when they gain little out of it
personally.

@@

\textcite{herley2009so} argued that users rationally reject costs
placed upon them from security policies. He invoked Kuhn's
``Paradigm Shift'' \parencite{kuhn1962structure} to suggest
an imminent, yet dramatic change in
how users are asked to authenticate as the complexity of
rules placed on users increases with each attack.

@@
